% LaTeX version of the departmental syllabus required for Spring 2013 and later,
% originally sent by Dr. Tam on Jan 1, 2013.

% Change the following variables and compile the document to create a PDF
% syllabus.
% Make sure syllabus_input.tex is in the same folder.

%%%%%%%%%%%%%%%%%%
% Mandatory Data %
%%%%%%%%%%%%%%%%%%

% Here's all the mandatory information you must provide
% (per departmental policy):

% Title stuff
  % Course Code, ex: MATH 1000-080
\newcommand{\CourseCode}{
MATH 2630-100/120
}
  % Course Name
\newcommand{\CourseName}{
Calculus III
}
  % Semester
\newcommand{\Semester}{
Spring 2015
}

% Instructor data
  % Your name
\newcommand{\InstName}{
Mr. Steven Clontz
}
  % Your office number
\newcommand{\OffLoc}{
Parker 140F
}
  % Your office hours
\newcommand{\OffHours}{
To be scheduled
}
  % Your office phone number
\newcommand{\OffPhone}{
N/A
}
  % Your email address
\newcommand{\Email}{
steven.clontz@auburn.edu
}

% Course data
  % Classroom location
\newcommand{\ClassLoc}{
Parker 326 / Parker 362
}
  % Lecture times (line 1)
\newcommand{\ClassTimeOne}{
MWF 1000-1050 / 1200-1250
}
  % Lecture times (line 2)
\newcommand{\ClassTimeTwo}{
R 0930-1020 / 1100-1150
}
  % Final exam time (line 1)
\newcommand{\FinalExamOne}{
Wed 2015-05-06 0800-1030 /
}
  % Final exam time (line 2)
\newcommand{\FinalExamTwo}{
Tues 2015-05-05 1200-1430
}
  % Number of credit hours
\newcommand{\CreditHrs}{
4
}
  % Textbook to be used
\newcommand{\Text}{
Instructor's notes
}

% Course Description
  % Automatically includes this text after your \CourseDesc message:
  %%%
  % (See also: http://bulletin.auburn.edu/coursesofinstruction/math/)
\newcommand{\CourseDesc}{
Multivariate calculus topics covered include: vector-valued functions,
partial derivatives, multiple integration, vector calculus.
}

% Grade Description
  % Written explanation of grading schema.
  % This is an EXAMPLE only. Current policy (2014-08-14) lets
  % instructors set own grading schema with approval by course coordinator.
  % Contact your course coordinator with any questions.
\newcommand{\GradeDesc}{
Grades for each student in this course are out of 1000 points, with letter
grades assigned as displayed on the chart below.
Up to 500 points may be earned through both group and individual work
throughout the semester. An individual final exam will be held at the end
of the semester which is worth 1000 points minus whatever has already been
earned.
}

% Grade Distribution
  % Table partitioning credit for each assignment
\newcommand{\GradeDist}{
\begin{tabular}{|l|l|}\hline
Diagonstic Exam* & 50 \\
Attendance & 50 \\
Packet/Test 1 & 100 \\
Packet/Test 2 & 100 \\
Packet/Test 3 & 100 \\
Packet/Test 4 & 100 \\
Final & 1000 - (pts earned) \\\hline\hline
Total & 1000 \\\hline
\end{tabular}
}

% Letter Grade Assignment
  % Table partitioning assignment of letter grades by percentage and points
\newcommand{\LetterAssign}{
\begin{tabular}{|c|c|c|}\hline
\bf{Grade} & \bf{Points} & \bf{Percentage}\\\hline\hline
A & 900-1000 & 90\% - 100\%\\
B & 800-899 & 80\% - 89\%\\
C & 700-799 & 70\% - 79\%\\
D & 650-699 & 65\% - 69\%\\
F & 0-649 & 0\% - 64\%\\\hline
\end{tabular}
}

% Makeup Policy
  % The default message is based on University policy.
  %
  % Automatically includes this text after your \MakeUp message:
  %%%
  % Details on Auburn University’s make up policy,
  % including a list of types of absences that are excused, may be found at
  % https://sites.auburn.edu/admin/universitypolicies/Policies/PolicyonClassAttendance.pdf

\newcommand{\MakeUp}{
Arrangements to make up missed exams due to excused absences must be
initiated by the student within one week from the end of the excused absence.
Group work may not be able to be made up, in which case it will be replaced with
comparable individual work.
}

% ADA Policy
  % Don't change this without good reason.
\newcommand{\ADA}{
Students who need accommodations are asked to electronically submit their
approved accommodations through AU Access and to arrange a meeting during
office hours the first week of classes, or as soon as possible if accommodations
are needed immediately. If you have not established accommodations through the
Office of Accessibility, but need accommodations, make an appointment with the
Office of Accessibility, 1228 Haley Center, 844-2096.
}

% Academic Honesty
  % Similarly, this probably shouldn't be changed.
\newcommand{\AcaHon}{
All portions of the Auburn University student academic honesty code (Title XII)\\
\centerline{\url{https://sites.auburn.edu/admin/universitypolicies/Policies/AcademicHonestyCode.pdf}}\\
will apply to this class. All academic honesty violations or alleged violations
of the SGA Code of Laws will be reported to the Office of the Provost, which
will then refer the case to the Academic Honesty Committee. \textbf{Tiger Cards
may be checked before any assignment is accepted.}
}

% Contingency Plan
  % The default setting allows you to change this syllabus as needed
  % (for example, giving one less exam due to time constraints),
  % but you should present the changed policy in writing to your class.
\newcommand{\ContPlan}{
If normal class and/or lab activities are disrupted due to illness, emergency,
or crisis situation, the syllabus and other course plans and assignments may be
modified to allow completion of the course. If this occurs, an addendum to your
syllabus and/or course assignments will replace the original materials.
}


%%%%%%%%%%%%%%%%%%%%%
% Optional Sections %
%%%%%%%%%%%%%%%%%%%%%

% Extra Sections
  % You can optionally add as many extra sections as you wish by editing the
  % \ExtraSections variable.
  % Set the variable as empty to remove these sections.
\newcommand{\ExtraSections}{
\textbf{Diagnostic Exam:} \\
The diagnostic exam will be written by stripping away Calculus III material
from a Calculus III final exam, leaving material from Precalculus (including
trigonometry) and Calculus I and II.
Students making below a 70\% will be given two opportunities to retake
a similar exam twice before midsemester (for a maximum
of 70\% credit). \textbf{*Since knowledge of this material
is critical for success in Calculus III,
a score of 70\% or higher on the diagnostic exam is required to
pass this course; all students with a score below 70\% will automatically
receive an F for the course.}

\textbf{Open Everything Policy:} \\
Textbooks, the internet, calculators, etc. are allowed to be used during
class time and all assessments (except for the diagnostic exam).
Two caveats: plagarism is unacceptable,
and you must show all work supporting material introduced in Calculus III to
receive credit.

\textbf{Study Groups:} \\
Each class will be divided into several Study Groups. Each study group will
work together on the course material, with some grades shared between
all members of each particular group (see below). In addition, each study
group is responsible for organizing a 60-minute Study Session outside of
regular class time. The instructor will join for roughly 30 minutes of this
session each week to function as office hours. Study Groups and Study Sessions
will be coordinated by the instructor with the input of the class, and
may change over the course of the semester.

\textbf{Attendance:} \\
Each student will earn up to 50 points for attendance, subtracting one point
for each unexcused absence, including absences from Study Sessions.

\textbf{Test/Packet Grades:}
The Test/Packet grades total to 100 points each. This grade is split into
four categories: Packet (20), Individual Test (30),
Group Test (30), and Teamwork (20).

\textbf{Packets:} \\
In lieu of a textbook, four packets of definitions, theorems, examples,
and problems will be provided. Each Study Group is responsible for typesetting
solutions to the given problems in \LaTeX{} to turn in before the corresponding
test. Some problems will be fully graded with partial credit, but others will
just be checked for completion.

\textbf{Individual Test:} \\
Each test begins with a 40 minute individual portion. All students will work
individually to complete their test, showing full work. All questions will be
fully graded with partial credit.

\newpage

\textbf{Group Test:} \\
Immediately following the individual test, an identical test will be given
for another 40 minutes, but members of each Study Group may now collaborate
with each other. However, solutions must still be written individually and
turned in separately.

\textbf{Teamwork:} \\
The instructor will assign each student credit for teamwork demonstrated since
the previous test, based on his best judgement.

\textbf{Final Exam:} \\
The Final Exam will be based on material from the four Tests/Packets. It will
be similar in structure to the previous Tests; however, there will not be
a group portion.

\textbf{Online materials:}\\
Much of the content for this course, as well as all grades, will be posted
online, either to Canvas or via a link from Canvas. To access Canvas, visit
\url{http://auburn.instructure.com/}.
}


% PostScript
  % You can optionally add a final comment at the end of the syllabus to
  % drive home an important point.
  % Set \PostScript as empty to remove this final comment.
  %
  % Automatically includes this text before your \PostScript messages:
  %%%
  % Please refer to the Student Policy eHandbook
  % http://www.auburn.edu/student_info/student_policies/
  % for more information - for example, what
  % to do if you have three or more finals scheduled on one day.
\newcommand{\PostScript}{}



\input{./syllabus_include.tex}

