\newcommand{\CourseCode}{ 
MATH 2630-080
}
  % Course Name
\newcommand{\CourseName}{
Calculus III
}
  % Semester
\newcommand{\Semester}{
Summer 2013
}

\input{../../syllabus_dochead.tex}

\begin{document}

\begin{center}
\textbf{\large \CourseCode | \CourseName | \Semester}

\textbf{Grading Overview - Steven Clontz}
\end{center}

\textbf{\large Quizzes}

At the beginning of class each Monday (Tuesday if class is not held on Monday), there will be a quiz over the homework from the previous week. The instructor will send an email each Thursday outlining which problems the quiz will be pulled from. All homework problems are posted on Canvas.

Each quiz is three questions, taken directly from the assigned homework, with no partial credit. Handwritten notes are allowed, but no printed materials or electronics may be used.

There will be ten quizzes total during the semester, making a total of 30 questions. You must answer 20 questions correctly by the end of the semester to receive full credit for the Quiz portion of your overall grade. If less quesitons are answered, the quiz grade will be the percentage of questions answered correctly out of 20. (For example, answering 16/30 questions correctly by the end of the semester results in a quiz grade of 16/20=75\%. Answering 22/30 questions correctly results in a quiz grade of 100\%.)

Students are encouraged to work with one another to work on homework, and/or to attend office hours. Students are discouraged from simply copying other students’ answers, as you won’t be prepared for the midterm or final exams if you do!

\textbf{\large Midterm Exam}

The midterm exam will be held during lecture the last day of the first minimester: \textbf{Wednesday, June 19, 8:00am-9:30am}. It will consist of 12 questions based upon all homework assigned as of the final quiz.

A few of the questions may be pulled directly from the homework, but most will be variations on the homework problems. Work must be shown on all problems, and partial credit will be given as follows: 10/10 points for a full solution, 9/10 for full solution with minor errors, 7/10 for a partial solution, 6/10 for a partial solution with minor errors, and 0/10 otherwise.

Points awarded for each problem will be added, and the percentage out of 120 points will be recorded as the midterm exam grade for each student.

\textbf{\large Final Exam}

The final exam will be held during the time appointed by the Provost: \textbf{Wednesday, July 31, 8:00am- 10:30am}. It will consist of 20 questions. 8 of these questions will be based upon the midterm exam, and 12 will be based upon other homework problems assigned since the midterm exam.

The final exam is constructed similarly to the midterm exam, and partial credit is also assigned similarly. Points awarded for each problem will be added, and the percentage out of 200 points will be recorded as the final exam grade for each student.

\center{\small{Last updated on \today}}

\end{document}